---
title: "Belay Buddy Demo"
body-class: yoga-project-page
---

::: {.yoga-view-toggle role="group" aria-label="Switch view"}
<button type="button" class="btn btn-primary yoga-btn-product" aria-pressed="true">Final product</button>
<button type="button" class="btn btn-outline-primary yoga-btn-overview" aria-pressed="false">Project Overview</button>
<button type="button" class="btn btn-outline-primary yoga-btn-scripts" aria-pressed="false">Scripts & Code</button>
:::

::: {#yoga-final-product .yoga-view-panel}
::: {.yoga-embed-bar}
[Open demo in new tab](demo.html){.btn .btn-sm .btn-outline-primary target="_blank" rel="noopener"}
:::
::: {#yoga-iframe-wrap .yoga-embed-full}
<iframe src="demo.html" title="Belay Buddy Demo — static web app" class="yoga-embed" allowfullscreen style="width:100%;height:100%;position:absolute;left:0;top:0;border:0;"></iframe>
:::
:::

::: {#yoga-overview .yoga-view-panel .d-none}
## Problem

When climbing with friends, managing climb/belay order gets messy quickly, especially when people join or leave during a long session. The goal of Belay Buddy is a fast, mobile-first workflow that keeps rotations fair and visible for the whole group without account setup.

## Approach

This portfolio page embeds a static demo for easy viewing, but the write-up here is based on the live production app codebase.

The production app is an R Shiny application with:

- host-created room sessions and quick host join
- add/remove participant flow with roster changes applied starting the next round
- 5-round "burst" display for now/upcoming rounds
- real pairing optimization (`lpSolve`) to reduce repeat pairings while maintaining role alternation when possible
- schedule download/share as standalone HTML backup

Core production files:

- `app.R` (UI/server flow and host UX)
- `R/session.R` (state, persistence, burst scheduling, sync)
- `R/pairing.R` (pair/trio optimization and role assignment)
- `R/html_export.R` (offline/shareable schedule export)

## Impact

- Used in real climbing sessions, not only as a prototype.
- Practical for free hosting: a static demo avoids runtime cost for portfolio visitors.
- Production app on free hosting can still hit limits (idle sleep/timeouts), so HTML export/share helps keep the group running even if the live instance pauses.
:::

::: {#yoga-scripts .yoga-view-panel .d-none}
## app.R {#script-app}

**What it does:** Main production Shiny entry point. Defines the host-first UI flow, session creation, participant management, next-round behavior, 5-round burst rendering, and schedule download/share controls.

```{r}
#| file: production_code/app.R
#| eval: false
```

---

## R/session.R {#script-session}

**What it does:** Session lifecycle and state backend. Persists shared room data (`session_store.rds`), synchronizes updates across clients, tracks roster events, handles burst creation (`ensure_burst`) and burst advancement (`advance_round_from_burst`), and manages backup-share flags.

```{r}
#| file: production_code/R/session.R
#| eval: false
```

---

## R/pairing.R {#script-pairing}

**What it does:** Pairing engine for top-rope rounds. Uses optimization with `lpSolve` to minimize repeat pairings, supports odd-group trios, and applies climb/belay/rest role preferences based on previous round actions.

```{r}
#| file: production_code/R/pairing.R
#| eval: false
```

---

## R/html_export.R {#script-html-export}

**What it does:** Builds standalone schedule HTML files that can be downloaded and shared (e.g., phone file share/WhatsApp) so the group can keep an offline copy if a free-hosted server instance sleeps.

```{r}
#| file: production_code/R/html_export.R
#| eval: false
```

---

:::

<script>
(function() {
  var productPanel = document.getElementById('yoga-final-product');
  var overviewPanel = document.getElementById('yoga-overview');
  var scriptsPanel = document.getElementById('yoga-scripts');
  var btnProduct = document.querySelector('.yoga-btn-product');
  var btnOverview = document.querySelector('.yoga-btn-overview');
  var btnScripts = document.querySelector('.yoga-btn-scripts');
  if (!productPanel || !overviewPanel || !scriptsPanel || !btnProduct || !btnOverview || !btnScripts) return;

  function setActive(btn) {
    [btnProduct, btnOverview, btnScripts].forEach(function(b) {
      b.classList.remove('btn-primary');
      b.classList.add('btn-outline-primary');
      b.setAttribute('aria-pressed', 'false');
    });
    btn.classList.add('btn-primary');
    btn.classList.remove('btn-outline-primary');
    btn.setAttribute('aria-pressed', 'true');
  }
  function showProduct() {
    productPanel.classList.remove('d-none');
    overviewPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    setActive(btnProduct);
  }
  function showOverview() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.remove('d-none');
    scriptsPanel.classList.add('d-none');
    setActive(btnOverview);
  }
  function showScripts() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    scriptsPanel.classList.remove('d-none');
    setActive(btnScripts);
  }

  btnProduct.addEventListener('click', showProduct);
  btnOverview.addEventListener('click', showOverview);
  btnScripts.addEventListener('click', showScripts);

  function buildMarginTOC() {
    if (!document.body.classList.contains('yoga-project-page')) return;
    var marginSidebar = document.getElementById('quarto-margin-sidebar');
    if (!marginSidebar || marginSidebar.querySelector('#TOC')) return;
    var main = document.getElementById('quarto-document-content');
    if (!main) return;
    var headings = main.querySelectorAll('h2.anchored[data-anchor-id]');
    if (headings.length === 0) return;
    var nav = document.createElement('nav');
    nav.id = 'TOC';
    nav.setAttribute('role', 'doc-toc');
    nav.className = 'toc-active';
    var title = document.createElement('h2');
    title.id = 'toc-title';
    title.textContent = 'On this page';
    nav.appendChild(title);
    var ul = document.createElement('ul');
    ul.className = 'collapse';
    headings.forEach(function(h2) {
      var id = h2.getAttribute('data-anchor-id') || h2.id;
      if (!id) return;
      var li = document.createElement('li');
      var a = document.createElement('a');
      a.href = '#' + id;
      a.id = 'toc-' + id;
      a.className = 'nav-link';
      a.setAttribute('data-scroll-target', '#' + id);
      a.textContent = h2.textContent.trim();
      li.appendChild(a);
      ul.appendChild(li);
    });
    nav.appendChild(ul);
    marginSidebar.appendChild(nav);
    document.querySelectorAll('#TOC a[data-scroll-target]').forEach(function(link) {
      link.addEventListener('click', function(e) {
        var id = link.getAttribute('data-scroll-target');
        if (!id) return;
        var target = document.querySelector(id);
        if (!target) return;
        if (overviewPanel.contains(target)) {
          e.preventDefault();
          showOverview();
          requestAnimationFrame(function() { target.scrollIntoView({ behavior: 'smooth' }); });
        } else if (scriptsPanel.contains(target)) {
          e.preventDefault();
          showScripts();
          requestAnimationFrame(function() { target.scrollIntoView({ behavior: 'smooth' }); });
        }
      });
    });
  }
  if (document.readyState === 'loading') {
    document.addEventListener('DOMContentLoaded', buildMarginTOC);
  } else {
    buildMarginTOC();
  }
})();
</script>
