---
title: "Belay Buddy Demo"
body-class: yoga-project-page
resources:
  - Belay_Buddy_Demo.mp4
  - exports/schedule-export-rounds-1-5.html
  - exports/schedule-export-rounds-4-8-after-roster-change.html
---

<div class="yoga-project-page-root" hidden aria-hidden="true"></div>

::: {.yoga-view-toggle role="group" aria-label="Switch view"}
<button type="button" class="btn btn-primary yoga-btn-product" aria-pressed="true">Final product</button>
<button type="button" class="btn btn-outline-primary yoga-btn-overview" aria-pressed="false">Project Overview</button>
<button type="button" class="btn btn-outline-primary yoga-btn-approach" aria-pressed="false">Project Approach</button>
<button type="button" class="btn btn-outline-primary yoga-btn-scripts" aria-pressed="false">Scripts & Code</button>
<button type="button" class="btn btn-outline-primary yoga-btn-impact" aria-pressed="false">Impact & Outcome</button>
:::

::: {#yoga-final-product .yoga-view-panel}

The **video** below is a screen recording of the **production** app with narration explaining how it works, using a single gym night as the through-line: a **13-person** top-rope session with an odd-count **trio**, then a **mid-session roster change** (the HTML exports at the bottom show **10 participants** and **rounds 4-8** after that change). Those **HTML schedule exports** match what participants can save or share when the live host pauses or the network drops.

### What the example shows (watch the video, then use this as a map)

1. **Host-led room** - The group starts with a full roster; the engine fills **rounds 1-5** with pairs and a **trio** so everyone rotates climb, belay, and rest roles fairly across the odd group.
2. **Visible burst** - Upcoming rounds stay in one place so the whole group shares the same plan (no whiteboard drift).
3. **Roster change before round 4** - Someone joins and several climbers leave early; the app records **effective-round** roster deltas (add **Mei**; remove **Amara**, **Michael**, **Daniel**, **Mo**).
4. **Re-optimized schedule** - Pairings from **round 4** onward reflect the smaller group; the second export is the **offline-friendly** snapshot for rounds **4-8** with the roster-change summary at the top.

### Demo video (production app)

```{=html}
<div class="yoga-embed-bar">
<a href="Belay_Buddy_Demo.mp4" class="btn btn-sm btn-outline-primary" download="Belay_Buddy_Demo.mp4">Download video (MP4)</a>
</div>
<div id="belay-video-frame-wrap">
<video controls playsinline preload="metadata" class="belay-demo-video">
  <source src="Belay_Buddy_Demo.mp4" type="video/mp4">
  <p>Your browser does not support embedded video. <a href="Belay_Buddy_Demo.mp4">Download the demo (MP4)</a>.</p>
</video>
</div>
```

### Offline schedule exports (HTML)

These are **browser-downloadable** schedule pages generated by the app (same styling as the live UI). **Left:** snapshot covering **rounds 1-5** with the initial **13** participants. **Right:** after the roster change, **rounds 4-8** for **10** participants, including the **Roster changes** card (effective round 4).

```{=html}
<div class="belay-schedule-embed-grid">
<div class="belay-schedule-embed-cell">
<p class="belay-schedule-embed-label"><strong>Rounds 1-5</strong> - initial roster (13 participants)</p>
<div class="belay-schedule-embed-wrap">
<iframe src="exports/schedule-export-rounds-1-5.html" title="Belay Buddy schedule export: rounds 1-5" class="belay-schedule-iframe"></iframe>
</div>
</div>
<div class="belay-schedule-embed-cell">
<p class="belay-schedule-embed-label"><strong>Rounds 4-8</strong> - after roster change (10 participants)</p>
<div class="belay-schedule-embed-wrap">
<iframe src="exports/schedule-export-rounds-4-8-after-roster-change.html" title="Belay Buddy schedule export: rounds 4-8 after roster change" class="belay-schedule-iframe"></iframe>
</div>
</div>
</div>
```

:::

::: {#yoga-overview .yoga-view-panel .d-none}
## Project Overview

### Problem

During top-rope sessions, **climb/belay order** falls apart when people join, leave, or swap roles. Whiteboards and ad hoc lists do not give everyone the same live view, and forcing sign-ups slows down casual groups.

### Context

The app is meant for **real gym nights**: mobile-first, fast to start, and usable without accounts. This portfolio page includes a **narrated demo video of the production app** plus **sample HTML schedule exports**; the narrative reflects the **production R Shiny** codebase.

### Goals

- Keep rotations **fair** and **visible** to the whole group.
- The app will try to preserve the following when possible:
  - **Diversity:** Participants will be paired at random without duplicating pairs
  - **Alternation:** Participants will alternate between climbing and belaying
  - **Trio aversion:** Participants will be placed in trios infrequently
- Support a **host-led** room model with quick participant join.
- Offer a **fallback** (downloadable schedule) when free-tier hosting sleeps or connectivity drops.

### Stakeholders

- **Climbing group** in a single session (host + participants).

### Final deliverable

- **Production:** Hosted R Shiny app with shared session state, burst scheduling, and pairing optimization.
- **Portfolio:** narrated **demo video** (production app) and embedded **HTML export** samples (no live Shiny embed). Implementation files and excerpts are under **Scripts & Code** (`app.R`, `R/session.R`, `R/pairing.R`, `R/html_export.R`). A small **static HTML prototype** (`demo.html`) remains in the project folder for reference.
:::

::: {#yoga-approach .yoga-view-panel .d-none}
## Project Approach

### Problem Definition

- **Context:** Top-rope nights **kept changing mid-session**-people joined, left, or swapped roles-and the group **had no** shared, fair rotation everyone could see.
- **Gap:** whiteboards and ad hoc lists **did not** scale; I also wanted to avoid **mandatory** accounts.

### Scope & Assumptions

- **Scope (planned):** lightweight **R Shiny** app; host-led rooms; **mobile-first** UI; a short “burst” of upcoming rounds; optional **HTML export** of the schedule.
- **Assumption:** typical group sizes stay small enough that `lpSolve` pairing will feel **instant** in-session.

### Data Sources

- **Planned state (minimal):** roster, recent pairings, roles, session metadata (server-side for sync).
- **Planned export:** standalone HTML participants can save or share if the live host sleeps.

### Analytical Design

- **Plan:** separate **optimization** from UI-`lpSolve`-backed engine to **minimize repeat pairings** while respecting climb / belay / rest alternation when possible; support **trios** when the group count is odd.
- **Product shape:** host-created rooms and quick host join; add/remove participants with roster changes taking effect on the **next** round; **5-round “burst”** UI for now/upcoming rounds; standalone **HTML export** for offline share.

### Workflow / Process

**Planned UX:** host opens room → roster locks in for the **next** round → engine proposes pairings → burst view shows near-future rounds → participants download/share HTML if the live host instance pauses or the network fails.

### Constraints & Considerations

- **Free-tier** hosting will mean cold starts and timeouts-I will design around that.
- **Host vs participant** paths must stay obvious.
- Export will be the **fallback** when the live instance pauses.
:::

::: {#yoga-scripts .yoga-view-panel .d-none}
## app.R {#script-app}

**What it does:** Main production Shiny entry point. Defines the host-first UI flow, session creation, participant management, next-round behavior, 5-round burst rendering, and schedule download/share controls.

```{r}
#| file: production_code/app.R
#| eval: false
```

---

## R/session.R {#script-session}

**What it does:** Session lifecycle and state backend. Persists shared room data (`session_store.rds`), synchronizes updates across clients, tracks roster events, handles burst creation (`ensure_burst`) and burst advancement (`advance_round_from_burst`), and manages backup-share flags.

```{r}
#| file: production_code/R/session.R
#| eval: false
```

---

## R/pairing.R {#script-pairing}

**What it does:** Pairing engine for top-rope rounds. Uses optimization with `lpSolve` to minimize repeat pairings, supports odd-group trios, and applies climb/belay/rest role preferences based on previous round actions.

```{r}
#| file: production_code/R/pairing.R
#| eval: false
```

---

## R/html_export.R {#script-html-export}

**What it does:** Builds standalone schedule HTML files that can be downloaded and shared (e.g., phone file share/WhatsApp) so the group can keep an offline copy if a free-hosted server instance sleeps.

```{r}
#| file: production_code/R/html_export.R
#| eval: false
```

---

:::

::: {#yoga-impact .yoga-view-panel .d-none}
## Impact & Outcome

Belay Buddy improved real-session coordination by making pairing decisions visible, fair, and easy to update as participants join or leave. The production app and static backup flow together make it resilient in low-cost hosting setups.

- **Who it helped:** Recreational climbing groups managing rotation logistics in real time.
- **What it helped with:** Reducing friction during sessions, minimizing repeated pairings, and maintaining continuity during connectivity or hosting interruptions.
- **Why it matters:** It turns a common coordination problem into a usable, repeatable operational workflow.
- **In production:** used in real sessions, not only as a prototype; the portfolio page uses a recorded walkthrough and downloadable-style HTML samples so visitors can review the UX without hosting the live app.

:::

<script>
(function() {
  var productPanel = document.getElementById('yoga-final-product');
  var overviewPanel = document.getElementById('yoga-overview');
  var approachPanel = document.getElementById('yoga-approach');
  var scriptsPanel = document.getElementById('yoga-scripts');
  var impactPanel = document.getElementById('yoga-impact');
  var btnProduct = document.querySelector('.yoga-btn-product');
  var btnOverview = document.querySelector('.yoga-btn-overview');
  var btnApproach = document.querySelector('.yoga-btn-approach');
  var btnScripts = document.querySelector('.yoga-btn-scripts');
  var btnImpact = document.querySelector('.yoga-btn-impact');
  if (!productPanel || !overviewPanel || !approachPanel || !scriptsPanel || !impactPanel || !btnProduct || !btnOverview || !btnApproach || !btnScripts || !btnImpact) return;

  function setActive(btn) {
    [btnProduct, btnOverview, btnApproach, btnScripts, btnImpact].forEach(function(b) {
      b.classList.remove('btn-primary');
      b.classList.add('btn-outline-primary');
      b.setAttribute('aria-pressed', 'false');
    });
    btn.classList.add('btn-primary');
    btn.classList.remove('btn-outline-primary');
    btn.setAttribute('aria-pressed', 'true');
  }
  function showProduct() {
    productPanel.classList.remove('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnProduct);
  }
  function showOverview() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.remove('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnOverview);
  }
  function showApproach() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.remove('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnApproach);
  }
  function showScripts() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.remove('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnScripts);
  }
  function showImpact() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.remove('d-none');
    setActive(btnImpact);
  }

  btnProduct.addEventListener('click', showProduct);
  btnOverview.addEventListener('click', showOverview);
  btnApproach.addEventListener('click', showApproach);
  btnScripts.addEventListener('click', showScripts);
  btnImpact.addEventListener('click', showImpact);
})();
</script>
