---
title: "Projects"
sidebar: false
execute:
  dir: project
format:
  html:
    number-sections: false
---

```{r}
#| label: load-projects
#| include: false
library(yaml)
# Works from project root (full render) or from projects/ (e.g. preview)
yaml_path <- if (file.exists("projects/projects.yaml")) "projects/projects.yaml" else "projects.yaml"
projects_list <- yaml.load_file(yaml_path)
if (is.null(projects_list$projects)) projects_list <- list(projects = list())
# Ensure each project has tags (character vector)
for (i in seq_along(projects_list$projects)) {
  p <- projects_list$projects[[i]]
  if (is.null(p$tags)) p$tags <- character(0)
  if (is.null(p$image)) p$image <- ""
  projects_list$projects[[i]] <- p
}

# Tag categories for the filter UI (order = display order)
# "Tech stack" = languages, frameworks, tools. "Methodology" = how you work. "Domain" = application area.
tag_categories <- list(
  list(name = "Tech stack", tags = c("R", "Python", "Quarto", "leaflet", "tidyverse")),
  list(name = "Methodology", tags = c("Automation", "ETL", "Web scraping")),
  list(name = "Domain", tags = c("Statistics", "Spatial", "Mapping", "Documentation", "Health data"))
)
```

```{r}
#| label: inject-projects-json
#| echo: false
#| results: asis
cat("<script type=\"application/json\" id=\"projects-data\">")
cat(jsonlite::toJSON(projects_list$projects, auto_unbox = TRUE))
cat("</script>\n")
cat("<script type=\"application/json\" id=\"tag-categories\">")
cat(jsonlite::toJSON(tag_categories, auto_unbox = TRUE))
cat("</script>\n")
```

```{=html}
<div class="projects-page" id="projects-page">
  <div class="projects-filters" id="projects-filters">
    <div class="projects-filter-groups" id="projects-filter-groups"></div>
    <button type="button" class="projects-clear-btn" id="projects-clear-btn" style="display: none;">Clear filters</button>
  </div>
  <p class="projects-count" id="projects-count"></p>
  <div class="projects-grid" id="projects-grid"></div>
  <p class="projects-empty" id="projects-empty" style="display: none;">No projects match the selected tags. Clear filters to see all.</p>
</div>
```

<script>
(function() {
  var dataEl = document.getElementById('projects-data');
  var catEl = document.getElementById('tag-categories');
  if (!dataEl || !catEl) return;
  var projects = JSON.parse(dataEl.textContent);
  var tagCategories = JSON.parse(catEl.textContent);
  var grid = document.getElementById('projects-grid');
  var filterGroupsEl = document.getElementById('projects-filter-groups');
  var countEl = document.getElementById('projects-count');
  var clearBtn = document.getElementById('projects-clear-btn');
  var emptyEl = document.getElementById('projects-empty');
  // Links are relative to projects/ (we're on projects/index.html), so no prefix
  var baseHref = '';

  var tagsInProjects = [];
  projects.forEach(function(p) {
    (p.tags || []).forEach(function(t) {
      if (tagsInProjects.indexOf(t) === -1) tagsInProjects.push(t);
    });
  });

  var tagToCategory = {};
  tagCategories.forEach(function(cat) {
    (cat.tags || []).forEach(function(t) { tagToCategory[t] = cat.name; });
  });
  var categoryOrder = tagCategories.map(function(cat) { return cat.name; });
  categoryOrder.push('Other');

  var state = { activeTags: [] };

  function toggleTag(tag) {
    var i = state.activeTags.indexOf(tag);
    if (i === -1) state.activeTags.push(tag);
    else state.activeTags.splice(i, 1);
    renderTagButtons();
    filterAndRender();
  }

  function clearFilters() {
    state.activeTags = [];
    renderTagButtons();
    filterAndRender();
  }

  function renderTagButtons() {
    filterGroupsEl.innerHTML = '';
    var byCategory = {};
    tagsInProjects.forEach(function(tag) {
      var cat = tagToCategory[tag] || 'Other';
      if (!byCategory[cat]) byCategory[cat] = [];
      byCategory[cat].push(tag);
    });
    categoryOrder.forEach(function(catName) {
      var tags = byCategory[catName];
      if (!tags || tags.length === 0) return;
      tags.sort();
      var group = document.createElement('div');
      group.className = 'projects-filter-group';
      var label = document.createElement('span');
      label.className = 'projects-filter-group-label';
      label.textContent = catName;
      group.appendChild(label);
      var list = document.createElement('div');
      list.className = 'projects-tag-list';
      tags.forEach(function(tag) {
        var btn = document.createElement('button');
        btn.type = 'button';
        btn.className = 'projects-tag-btn' + (state.activeTags.indexOf(tag) !== -1 ? ' active' : '');
        btn.textContent = tag;
        btn.addEventListener('click', function() { toggleTag(tag); });
        list.appendChild(btn);
      });
      group.appendChild(list);
      filterGroupsEl.appendChild(group);
    });
    clearBtn.style.display = state.activeTags.length > 0 ? 'inline-block' : 'none';
  }

  function filteredProjects() {
    if (state.activeTags.length === 0) return projects.slice();
    return projects.filter(function(p) {
      var pt = p.tags || [];
      return state.activeTags.some(function(t) { return pt.indexOf(t) !== -1; });
    });
  }

  function filterAndRender() {
    var list = filteredProjects();
    countEl.textContent = list.length + ' project' + (list.length !== 1 ? 's' : '');
    emptyEl.style.display = list.length === 0 ? 'block' : 'none';
    grid.innerHTML = '';
    list.forEach(function(p) {
      var raw = (p.href || '').trim();
      var href = raw.indexOf('/') === 0 ? raw : (baseHref + raw);
      var card = document.createElement('article');
      card.className = 'projects-card';
      card.setAttribute('data-tags', (p.tags || []).join(','));
      var visual = '';
      if (p.image && p.image.trim()) {
        visual = '<div class="projects-card-visual"><img src="' + p.image.replace(/"/g, '&quot;') + '" alt="" loading="lazy"></div>';
      } else {
        visual = '<div class="projects-card-visual"><span class="projects-card-visual-placeholder" aria-hidden="true">◇</span></div>';
      }
      var titleEsc = (p.title || 'Project').replace(/</g, '&lt;').replace(/>/g, '&gt;');
      var descEsc = (p.description || '').replace(/</g, '&lt;').replace(/>/g, '&gt;').replace(/"/g, '&quot;');
      var tagHtml = (p.tags || []).map(function(t) {
        return '<span class="projects-card-tag filter-tag" data-tag="' + t.replace(/"/g, '&quot;') + '">' + t.replace(/</g, '&lt;') + '</span>';
      }).join('');
      card.innerHTML =
        visual +
        '<div class="projects-card-body">' +
          '<h3 class="projects-card-title"><a href="' + href.replace(/"/g, '&quot;') + '">' + titleEsc + '</a></h3>' +
          '<p class="projects-card-desc">' + descEsc + '</p>' +
          '<div class="projects-card-tags">' + tagHtml + '</div>' +
        '</div>';
      card.querySelectorAll('.projects-card-tag.filter-tag').forEach(function(t) {
        t.addEventListener('click', function(e) {
          e.preventDefault();
          toggleTag(t.getAttribute('data-tag'));
        });
      });
      grid.appendChild(card);
    });
  }

  clearBtn.addEventListener('click', clearFilters);
  renderTagButtons();
  filterAndRender();
})();
</script>
