---
title: "Projects"
sidebar: false
execute:
  dir: project
format:
  html:
    toc: false
    page-layout: full
    number-sections: false
---

::: {.projects-hero-section}

[Projects]{.projects-hero-kicker}

These projects reflect how I approach analytical and research work: clarity, structure, reproducibility, and practical outcomes.

Explore my work by theme - use the filters to narrow by tools, capabilities, and delivery.

:::

```{r}
#| label: load-projects
#| include: false
library(yaml)
# Works from project root (full render) or from projects/ (e.g. preview)
yaml_path <- if (file.exists("projects/projects.yaml")) "projects/projects.yaml" else "projects.yaml"
projects_list <- yaml.load_file(yaml_path)
if (is.null(projects_list$projects)) projects_list <- list(projects = list())
# Ensure each project has tags (character vector)
for (i in seq_along(projects_list$projects)) {
  p <- projects_list$projects[[i]]
  if (is.null(p$tags)) p$tags <- character(0)
  if (is.null(p$image)) p$image <- ""
  projects_list$projects[[i]] <- p
}

# Tag categories for the filter UI (order = display order).
# Tools & stack: languages, HTML+CSS, Quarto, R Shiny, GIS (no per-package tags).
# Capabilities: what the work demonstrates. Delivery & impact: kind of value / artifact.
tag_categories <- list(
  list(name = "Tools & stack", tags = c("R", "Python", "JavaScript", "HTML+CSS", "Quarto", "R Shiny", "GIS")),
  list(name = "Capabilities", tags = c(
    "Spatial", "Mapping & visualization", "Statistics", "Data integration & ETL",
    "Interactive tools", "Automation", "Web scraping", "Documentation", "Privacy-conscious workflows"
  )),
  list(name = "Delivery & impact", tags = c("Research synthesis", "Operational tooling", "Teaching / enablement"))
)

# Default card art: SVG per Delivery & impact tag (paths relative to site root; JS adds ../ on projects/index.html)
delivery_icon_map <- list(
  "Research synthesis" = "assets/project-icons/delivery/research-synthesis.svg",
  "Operational tooling" = "assets/project-icons/delivery/operational-tooling.svg",
  "Teaching / enablement" = "assets/project-icons/delivery/teaching-enablement.svg"
)
```

```{r}
#| label: inject-projects-json
#| echo: false
#| results: asis
cat("<script type=\"application/json\" id=\"projects-data\">")
cat(jsonlite::toJSON(projects_list$projects, auto_unbox = TRUE))
cat("</script>\n")
cat("<script type=\"application/json\" id=\"tag-categories\">")
cat(jsonlite::toJSON(tag_categories, auto_unbox = TRUE))
cat("</script>\n")
cat("<script type=\"application/json\" id=\"delivery-icon-map\">")
cat(jsonlite::toJSON(delivery_icon_map, auto_unbox = TRUE))
cat("</script>\n")
```

```{=html}
<div class="projects-page" id="projects-page">
  <div class="projects-filters" id="projects-filters">
    <div class="projects-filter-groups" id="projects-filter-groups"></div>
    <button type="button" class="projects-clear-btn" id="projects-clear-btn" style="display: none;">Clear filters</button>
  </div>
  <p class="projects-count" id="projects-count"></p>
  <div class="projects-grid" id="projects-grid"></div>
  <p class="projects-empty" id="projects-empty" style="display: none;">No projects match the selected tags. Clear filters to see all.</p>
</div>
```

<script>
(function() {
  var dataEl = document.getElementById('projects-data');
  var catEl = document.getElementById('tag-categories');
  var deliveryMapEl = document.getElementById('delivery-icon-map');
  if (!dataEl || !catEl || !deliveryMapEl) return;
  var projects = JSON.parse(dataEl.textContent);
  var tagCategories = JSON.parse(catEl.textContent);
  var deliveryIconMap = JSON.parse(deliveryMapEl.textContent);
  // First matching tag wins (stable priority if a project ever has multiple delivery tags)
  var deliveryTagPriority = ['Research synthesis', 'Operational tooling', 'Teaching / enablement'];
  var grid = document.getElementById('projects-grid');
  var filterGroupsEl = document.getElementById('projects-filter-groups');
  var countEl = document.getElementById('projects-count');
  var clearBtn = document.getElementById('projects-clear-btn');
  var emptyEl = document.getElementById('projects-empty');
  // Links are relative to projects/ (we're on projects/index.html), so no prefix
  var baseHref = '';

  var tagsInProjects = [];
  projects.forEach(function(p) {
    (p.tags || []).forEach(function(t) {
      if (tagsInProjects.indexOf(t) === -1) tagsInProjects.push(t);
    });
  });

  var tagToCategory = {};
  tagCategories.forEach(function(cat) {
    (cat.tags || []).forEach(function(t) { tagToCategory[t] = cat.name; });
  });
  var categoryOrder = tagCategories.map(function(cat) { return cat.name; });
  categoryOrder.push('Other');

  var state = { activeTags: [] };

  function toggleTag(tag) {
    var i = state.activeTags.indexOf(tag);
    if (i === -1) state.activeTags.push(tag);
    else state.activeTags.splice(i, 1);
    renderTagButtons();
    filterAndRender();
  }

  function clearFilters() {
    state.activeTags = [];
    renderTagButtons();
    filterAndRender();
  }

  function renderTagButtons() {
    filterGroupsEl.innerHTML = '';
    var byCategory = {};
    tagsInProjects.forEach(function(tag) {
      var cat = tagToCategory[tag] || 'Other';
      if (!byCategory[cat]) byCategory[cat] = [];
      byCategory[cat].push(tag);
    });
    categoryOrder.forEach(function(catName) {
      var tags = byCategory[catName];
      if (!tags || tags.length === 0) return;
      tags.sort();
      var group = document.createElement('div');
      group.className = 'projects-filter-group';
      var label = document.createElement('span');
      label.className = 'projects-filter-group-label';
      label.textContent = catName;
      group.appendChild(label);
      var list = document.createElement('div');
      list.className = 'projects-tag-list';
      tags.forEach(function(tag) {
        var btn = document.createElement('button');
        btn.type = 'button';
        btn.className = 'projects-tag-btn' + (state.activeTags.indexOf(tag) !== -1 ? ' active' : '');
        btn.textContent = tag;
        btn.addEventListener('click', function() { toggleTag(tag); });
        list.appendChild(btn);
      });
      group.appendChild(list);
      filterGroupsEl.appendChild(group);
    });
    clearBtn.style.display = state.activeTags.length > 0 ? 'inline-block' : 'none';
  }

  function escapeAttr(s) {
    return String(s).replace(/&/g, '&amp;').replace(/"/g, '&quot;').replace(/</g, '&lt;');
  }

  function resolveCardVisual(p) {
    if (p.image && String(p.image).trim()) {
      var title = (p.title || 'Project');
      return {
        html: '<div class="projects-card-visual"><img src="' + escapeAttr(p.image.trim()) + '" alt="' + escapeAttr(title) + '" loading="lazy"></div>'
      };
    }
    var tags = p.tags || [];
    var rel = null;
    var altLabel = '';
    for (var i = 0; i < deliveryTagPriority.length; i++) {
      var dt = deliveryTagPriority[i];
      if (tags.indexOf(dt) !== -1 && deliveryIconMap[dt]) {
        rel = deliveryIconMap[dt];
        altLabel = dt;
        break;
      }
    }
    if (rel) {
      var src = rel.indexOf('/') === 0 || /^(https?:|data:)/i.test(rel) ? rel : ('../' + rel);
      return {
        html: '<div class="projects-card-visual projects-card-visual--delivery-icon"><img src="' + escapeAttr(src) + '" alt="' + escapeAttr(altLabel) + '" loading="lazy"></div>'
      };
    }
    return {
      html: '<div class="projects-card-visual"><span class="projects-card-visual-placeholder" aria-hidden="true">◇</span></div>'
    };
  }

  function filteredProjects() {
    if (state.activeTags.length === 0) return projects.slice();
    return projects.filter(function(p) {
      var pt = p.tags || [];
      return state.activeTags.some(function(t) { return pt.indexOf(t) !== -1; });
    });
  }

  function filterAndRender() {
    var list = filteredProjects();
    countEl.textContent = list.length + ' project' + (list.length !== 1 ? 's' : '');
    emptyEl.style.display = list.length === 0 ? 'block' : 'none';
    grid.innerHTML = '';
    list.forEach(function(p) {
      var raw = (p.href || '').trim();
      var href = raw.indexOf('/') === 0 ? raw : (baseHref + raw);
      var card = document.createElement('article');
      card.className = 'projects-card';
      card.setAttribute('data-tags', (p.tags || []).join(','));
      var visual = resolveCardVisual(p).html;
      var titleEsc = (p.title || 'Project').replace(/</g, '&lt;').replace(/>/g, '&gt;');
      var descEsc = (p.description || '').replace(/</g, '&lt;').replace(/>/g, '&gt;').replace(/"/g, '&quot;');
      var tagHtml = (p.tags || []).map(function(t) {
        return '<span class="projects-card-tag filter-tag" data-tag="' + t.replace(/"/g, '&quot;') + '">' + t.replace(/</g, '&lt;') + '</span>';
      }).join('');
      card.innerHTML =
        visual +
        '<div class="projects-card-body">' +
          '<h3 class="projects-card-title"><a href="' + href.replace(/"/g, '&quot;') + '">' + titleEsc + '</a></h3>' +
          '<p class="projects-card-desc">' + descEsc + '</p>' +
          '<div class="projects-card-tags">' + tagHtml + '</div>' +
        '</div>';
      card.querySelectorAll('.projects-card-tag.filter-tag').forEach(function(t) {
        t.addEventListener('click', function(e) {
          e.preventDefault();
          toggleTag(t.getAttribute('data-tag'));
        });
      });
      grid.appendChild(card);
    });
  }

  clearBtn.addEventListener('click', clearFilters);
  renderTagButtons();
  filterAndRender();
})();
</script>
