---
title: "Leaflet Map Demo"
---

## Interactive map (placeholder)

This page shows an **R + leaflet** map embedded in Quarto. The code uses **tidyverse** to build a small data set and **leaflet** to render an interactive map. Replace the data and styling with your own project.

## Data (tidyverse)

We create a minimal tibble of placeholder locations. In a real project you might read from CSV, shapefiles, or an API.

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(leaflet)
```

```{r}
#| label: data
#| echo: true
sites <- tibble(
  name = c("Site A", "Site B", "Site C"),
  lat  = c(40.71, 40.75, 40.68),
  lng  = c(-74.01, -73.98, -74.05),
  value = c(10, 25, 15)
)
sites
```

## Map (leaflet)

```{r}
#| label: map
#| fig-cap: "Placeholder interactive map — replace with your own locations and basemap."
leaflet(sites) %>%
  addTiles() %>%
  addCircleMarkers(
    lng = ~lng,
    lat = ~lat,
    radius = ~value,
    popup = ~paste0("<b>", name, "</b><br>Value: ", value),
    color = "#2c3e50",
    fillColor = "#3498db",
    fillOpacity = 0.6,
    weight = 1
  ) %>%
  setView(lng = -74.0, lat = 40.72, zoom = 11)
```

## Next steps

*Placeholder: Describe how you’d extend this (e.g., real coordinates, custom tiles, or links to full code).*

- Swap `sites` for your own sf or tibble of points.
- Use `addProviderTiles()` for different basemaps (e.g. `"CartoDB.Positron"`).
- Add polygons or lines with `addPolygons()` / `addPolylines()` and **sf** objects.
