---
title: "Leaflet Mapping Tool"
---

<div class="yoga-project-page-root" hidden aria-hidden="true"></div>

::: {.yoga-view-toggle role="group" aria-label="Switch view"}
<button type="button" class="btn btn-primary yoga-btn-product" aria-pressed="true">Final product</button>
<button type="button" class="btn btn-outline-primary yoga-btn-overview" aria-pressed="false">Project Overview</button>
<button type="button" class="btn btn-outline-primary yoga-btn-approach" aria-pressed="false">Project Approach</button>
<button type="button" class="btn btn-outline-primary yoga-btn-scripts" aria-pressed="false">Scripts & Code</button>
<button type="button" class="btn btn-outline-primary yoga-btn-impact" aria-pressed="false">Impact & Outcome</button>
:::

::: {#yoga-final-product .yoga-view-panel}
::: {.yoga-embed-bar}
[Open project in new tab](vignettes/vignettes.html){.btn .btn-sm .btn-outline-primary target="_blank" rel="noopener"}
:::
::: {#yoga-iframe-wrap .yoga-embed-full}
<iframe src="vignettes/vignettes.html" title="Leaflet Mapping Tool - vignettes" class="yoga-embed" allowfullscreen style="width:100%;height:100%;position:absolute;left:0;top:0;border:0;"></iframe>
:::
:::

::: {#yoga-overview .yoga-view-panel .d-none}
## Project Overview

### Problem

A Statistics Canada field team needed neighbourhood-level context to support **months-long** data collection across **16 Canadian cities**. Each city called for many map views (building-level detail, multiple neighbourhoods, safety-related planning), but producing **50+ static maps per city** was slow, hard to update, and depended on GIS specialists.

### Context

Maps must refresh on roughly a **two-year** survey cycle. Staff who support the field program have strong domain skills but are not GIS power users, so the client needed something **reproducible** and teachable.

### Goals

- Replace binders of static exports with **one interactive map per city** (zoom, pan, basemap switch, layer toggles, informative popups).
- Standardize logic across cities so every place runs the **same** pipeline.
- Make routine updates runnable by analysts with **basic R** skills.

### Stakeholders

- **Primary:** Statistics Canada field teams and the analysts who prepare their mapping products.
- **Portfolio visitors:** see a public demo that uses non-sensitive layers while showing the same architecture.

### Final deliverable

An **R + Leaflet** workflow driven by OpenStreetMap and census boundaries: configurable per city or bbox, with optional bivariate views. The embedded vignette is the live demo; scripts and setup are under **Scripts & Code** (see also the project [Guide](guide.qmd)).

### Note on the public demo

Safety and crime indicators are not public, so this portfolio build demonstrates the tool with **median household income** and **greenspace** access. The internal workflow supports swapping in the operational layers when data policy allows.

If you are interested in adapting this tool for your own project, feel free to reach out.
:::

::: {#yoga-approach .yoga-view-panel .d-none}
## Project Approach

### Problem Definition

- **Context:** Field teams needed **neighbourhood-level** context across many Canadian cities on a **repeat** cadence.
- **What wasn’t working:** the old workflow leaned on **dozens of static maps** per city and on GIS specialists for routine updates-it **did not** scale.

### Scope & Assumptions

- **Scope (planned):** one **R-based**, reproducible workflow-OSM + census layers-runnable by analysts with basic R.
- **Public demo (planned):** income + greenspace will stand in for sensitive layers; the architecture will **swap in** real indicators when internal data are available.

### Data Sources

- **Planned:** StatCan DA boundaries + census income (SES); OSM greenspace / context; bbox per city or custom study area.
- **Caching** where possible so I do not hammer Overpass on every run.

### Analytical Design

- **Deliverable shape:** **one interactive Leaflet map per city** (not a binder of static exports).
- **Rules:** shared config (`map_config`, SES build, green-by-DA) so every city follows the **same** logic.
- **Optional:** a bivariate view when it strengthens the story.
- **Interaction model:** zooming, panning, basemap switching, layer toggles, and click-to-reveal popups replace the old static map set.

### Workflow / Process

**Planned flow:** resolve bbox (city name or custom) → clip dissemination areas and SES → fetch/cache OSM greenspace (respecting Overpass limits) → classify → render with **one legend system** → repeat each survey cycle with minimal manual steps. End-to-end automation so non-GIS analysts can regenerate maps without redrawing exports by hand.

### Constraints & Considerations

- Overpass **rate limits**; scripts must stay **offline-repeatable**.
- A public portfolio build **will not** ship safety/crime layers-demo layers will **showcase** the pipeline without exposing restricted data.
:::

::: {#yoga-scripts .yoga-view-panel .d-none}
## create_bivariate_map.R {#script-create-bivariate-map}

**What it does:** Main entry point for the bivariate map. Builds an **Income × Green area per 1,000 people** Leaflet map for a given city or custom bbox. Sources map_config, process_bbox, and process_green_da; clips DAs to the study area, fetches OSM greenspace (with optional walkable buffer), classifies income and greenspace into Low/Med/High (mean ± 1 SD), and renders a 3×3 bivariate choropleth with popups and legend. Supports custom_bbox, custom_distance_km, green_buffer_m, and show_green_layers.

```{r}
#| file: R/create_bivariate_map.R
#| eval: false
```

---

## mapping_functions.R {#script-mapping-functions}

**What it does:** Helper functions for the Leaflet map: `create_custom_icon`, `add_markers_conditionally`, `add_polylines_conditionally`, and `add_polygons_conditionally` to add OSM features (parks, playgrounds, nature, etc.) as toggleable layers with popups. Used when `show_green_layers = TRUE`.

```{r}
#| file: R/mapping_functions.R
#| eval: false
```

---

## map_config.R {#script-map-config}

**What it does:** Central configuration list for SES (income) categories and green-space settings. Defines `ses` (labels, colours, emoji, SD multipliers for 5 income bands) and `green` (thresholds for Limited/Good/Great, icon URLs for parks/playgrounds/nature). Used by build_ses_index.R and process_green.R; create_bivariate_map.R uses its own bivariate palette.

```{r}
#| file: R/map_config.R
#| eval: false
```

---

## process_green_da.R {#script-process-green-da}

**What it does:** Computes green area per dissemination area (and per 1,000 people). For each DA, sums OSM greenspace (parks, gardens, meadows, etc.) inside the DA plus within a walkable buffer (e.g. 500 m). Fetches OSM for the study bbox, merges polygon types, intersects with buffered DAs, and returns DAs with `green_area_m2` and `green_area_per_1000`. Handles Overpass rate limiting and uses cache_utils for optional caching.

```{r}
#| file: R/process_green_da.R
#| eval: false
```

---

## process_green.R {#script-process-green}

**What it does:** Fetches OSM green-space data (parks, playgrounds, nature reserves) for a given bbox and returns a list with green_status (Limited/Good/Great by count), plus sf layers for parks, playgrounds, and nature (as centroids for markers). Used for green-status summaries or optional marker layers; create_bivariate_map uses process_green_da for per-DA green area.

```{r}
#| file: R/process_green.R
#| eval: false
```

---

## build_ses_index.R {#script-build-ses-index}

**What it does:** Builds the income/SES GeoPackage from Statistics Canada 2021 Census and DA boundaries. Reads census CSV(s) and boundary shapefiles from data/raw/, joins on DA code, computes median household income and optional SES index (mean ± SD bands), and writes data/ses_index.gpkg. Supports test mode (one region, limited rows). Run after fetch_statcan_census.py (or equivalent) has downloaded and extracted census and boundaries.

```{r}
#| file: R/build_ses_index.R
#| eval: false
```

---

## process_bbox.R {#script-process-bbox}

**What it does:** Resolves the study-area bounding box (from city name via osmdata::getbb, custom_bbox, or amalgamation_cities_list), optionally expands it by custom_distance_km, clips the income GeoPackage to the bbox, and writes clipped polygons to data/clipped_income/. Caches clipped layer by bbox UID in data/cache.gpkg. Returns bbox matrix and paths needed by create_bivariate_map.

```{r}
#| file: R/process_bbox.R
#| eval: false
```

---

## cache_utils.R {#script-cache-utils}

**What it does:** GeoPackage cache utilities for clipped_income, greenspace, and buffered DAs. `bbox_to_uid()` generates a stable UID from bbox coordinates; `ensure_cache()` creates the cache file and empty layers; read/write helpers avoid re-fetching OSM or re-clipping when the same bbox (and buffer) has already been processed. Reduces Overpass load and speeds up repeated runs.

```{r}
#| file: R/cache_utils.R
#| eval: false
```

---

See the [Guide](guide.qmd) in this project for setup and how to run the tool.
:::

::: {#yoga-impact .yoga-view-panel .d-none}
## Impact & Outcome

This tool changed how field-support mapping was delivered for recurring surveys. It reduced manual map production overhead, helped non-GIS analysts generate consistent outputs, and made update cycles substantially easier to maintain over time.

- **Who it helped:** Statistics Canada field teams and analysts supporting multi-city data collection.
- **What it helped with:** Faster situational planning, standardized map logic, and improved reproducibility across survey cycles.
- **Why it matters:** It converted a specialist-dependent workflow into an operational tool that can be rerun and adapted as requirements evolve.
:::

<script>
(function() {
  var productPanel = document.getElementById('yoga-final-product');
  var overviewPanel = document.getElementById('yoga-overview');
  var approachPanel = document.getElementById('yoga-approach');
  var scriptsPanel = document.getElementById('yoga-scripts');
  var impactPanel = document.getElementById('yoga-impact');
  var btnProduct = document.querySelector('.yoga-btn-product');
  var btnOverview = document.querySelector('.yoga-btn-overview');
  var btnApproach = document.querySelector('.yoga-btn-approach');
  var btnScripts = document.querySelector('.yoga-btn-scripts');
  var btnImpact = document.querySelector('.yoga-btn-impact');
  if (!productPanel || !overviewPanel || !approachPanel || !scriptsPanel || !impactPanel || !btnProduct || !btnOverview || !btnApproach || !btnScripts || !btnImpact) return;

  function setActive(btn) {
    [btnProduct, btnOverview, btnApproach, btnScripts, btnImpact].forEach(function(b) {
      b.classList.remove('btn-primary');
      b.classList.add('btn-outline-primary');
      b.setAttribute('aria-pressed', 'false');
    });
    btn.classList.add('btn-primary');
    btn.classList.remove('btn-outline-primary');
    btn.setAttribute('aria-pressed', 'true');
  }
  function showProduct() {
    productPanel.classList.remove('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnProduct);
  }
  function showOverview() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.remove('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnOverview);
  }
  function showApproach() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.remove('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnApproach);
  }
  function showScripts() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.remove('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnScripts);
  }
  function showImpact() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.remove('d-none');
    setActive(btnImpact);
  }

  btnProduct.addEventListener('click', showProduct);
  btnOverview.addEventListener('click', showOverview);
  btnApproach.addEventListener('click', showApproach);
  btnScripts.addEventListener('click', showScripts);
  btnImpact.addEventListener('click', showImpact);
})();
</script>
