---
title: "Yoga Video Catalog"
---

<div class="portfolio-project-page-root" hidden aria-hidden="true"></div>

::: {.portfolio-view-toggle role="group" aria-label="Switch view"}
<button type="button" class="btn btn-primary portfolio-btn-product" aria-pressed="true">Final product</button>
<button type="button" class="btn btn-outline-primary portfolio-btn-overview" aria-pressed="false">Project Overview</button>
<button type="button" class="btn btn-outline-primary portfolio-btn-approach" aria-pressed="false">Project Approach</button>
<button type="button" class="btn btn-outline-primary portfolio-btn-scripts" aria-pressed="false">Scripts & Code</button>
<button type="button" class="btn btn-outline-primary portfolio-btn-impact" aria-pressed="false">Impact & Outcome</button>
:::

::: {.portfolio-page-intro}
::: {.portfolio-accent-rule}
:::
Automated cross-channel catalog pipeline that turns raw YouTube listings into a practical, filterable yoga videos.
:::

::: {.portfolio-meta-row}
[Media catalog automation]{.portfolio-meta-chip}
[Metadata standardization at scale]{.portfolio-meta-chip}
[Filterable content library]{.portfolio-meta-chip}
:::

::: {#portfolio-final-product .portfolio-view-panel}
::: {.portfolio-embed-bar}
[Open project in new tab](browse.html){.btn .btn-sm .btn-outline-primary target="_blank" rel="noopener"}
:::
::: {#portfolio-iframe-wrap .portfolio-embed-full}
<iframe src="browse.html" title="Yoga Video Catalog - browse" class="portfolio-embed" allowfullscreen style="width:100%;height:100%;position:absolute;left:0;top:0;border:0;"></iframe>
:::
:::

::: {#portfolio-overview .portfolio-view-panel .d-none}
## Project Overview

### Problem

As a regular climber with office-heavy workdays, yoga became a practical way to maintain flexibility and mobility while offsetting long stretches of sitting. Over time, preferred channels and flow styles became clear, but YouTube's broad, general-purpose search experience made it difficult to filter yoga content with the granularity needed for real session planning.

### Context

The project started as a personal frustration: repeatedly searching multiple channels for combinations like duration, body-focus intent, recency, and instructor. The goal was to build a focused catalog for trusted channels that stays current as new videos are published, without hand-maintained spreadsheets or YouTube API setup.

### Goals

- Centralize videos from a configurable channel list in one browsable catalog.
- Support the actual browse interactions implemented in the app: dual-range duration and upload-year controls, include/exclude chips for focus and channel, keyword search, hover preview, and a browser-persisted My List queue.
- Keep updates automated and reproducible (scrape -> enrich -> categorize -> focus refresh -> publish), not copy-paste.

### Stakeholders

- **Primary user:** me, for day-to-day practice planning.
- **Secondary users:** climbing friends who want more targeted filtering than default platform search.
- **Portfolio audience:** visitors evaluating end-to-end data engineering and front-end delivery.

### Final deliverable

The [Browse catalog](browse.html) is the main product: a full-screen, filterable HTML catalog backed by the enriched CSV, with duration and year range controls, focus and channel include/exclude chips, keyword search, in-card video preview, and a localStorage-backed queue with reorder and total-duration summaries. Implementation details, scripts, and data paths live under Scripts & Code.
:::

:::: {#portfolio-approach .portfolio-view-panel .d-none}
## Project Approach

### Problem Definition

- **Context:** Yoga videos lived across several channels; there was no single place to filter by length, body focus, or recency.
- **Gap:** Repeated manual searching and cross-checking across channels replaced what should have been one reusable, yoga-specific browse layer.

### Scope & Assumptions

- **Scope:** personal-use catalog with an open workflow, reproducible automation, and a fixed list of trusted channels managed in configuration.
- **Assumptions:** channel layouts will stay scrapable; yt-dlp metadata will be enough to tag focus without hand-labeling every video.

### Data Sources

- **Inputs:** listing fields from each channel's Videos page (video IDs, titles, durations, metadata line, URL) plus per-video metadata fetched with yt-dlp (description, upload date, view count, like count, categories, tags).
- **Config-only tuning:** `channel_urls.json`, `focus_map.json`, `exclude_keywords.json` (change without editing code).
- **Artifacts:** enriched CSV is the source of truth; Quarto `browse.qmd` reads it and emits JSON payloads for the static browse UI.

### Analytical Design

- **Intent:** a pipeline, not a one-off scrape - incremental "new videos only" pulls per channel.
- **Focus rules:** deterministic keyword matching on title + truncated description (using `focus_map.json`) to assign canonical focus tags.
- **Derived fields:** duration minutes and buckets, upload-year fields, and view-count bands for consistent filtering and presentation.
- **Stack:** Python + Playwright for listings, yt-dlp + pandas for enrichment and categorization, and Quarto + R + vanilla JS for browse-page rendering and client-side interaction - no YouTube API authentication flow required.

### Workflow / Process

End-to-end flow from channel list to live catalog:

| Step | What it does |
|------|----------------|
| **1. Configure** | Channel list in `data/channel_urls.json` (display name → channel Videos page URL). |
| **2. Scrape** | `scrape_channel.py` uses Playwright to open each channel’s Videos page, scroll to load items, extract video IDs, titles, durations. |
| **3. Enrich** | `enrich_videos.py` uses yt-dlp for metadata and derives **focus** from title/description via `focus_map.json`. |
| **4. Categorize** | `categorize_data.py` adds duration buckets, upload year, view-count bands. |
| **5. Focus** | `update_focus.py` refreshes focus after config changes (no re-fetch). |
| **6. Update (orchestrator)** | `update_from_channels.py` pulls only **new** videos per channel, appends, then categorizes and updates focus on the full file. |
| **7. Publish** | Render `browse.qmd` so HTML reflects the latest `yoga_videos_enriched.csv`. |

So: scraping -> ETL -> categorization -> focus -> Quarto render in one repeatable path.

### Constraints & Considerations

- Site terms and request pacing still matter even without API keys.
- YouTube layout changes can break selectors and require periodic scraper maintenance.
- Keyword maps and exclusion lists improve consistency, but they are heuristic and need occasional review as channels and naming patterns evolve.
::::

:::: {#portfolio-scripts .portfolio-view-panel .d-none}
## Data and config

| Path | Purpose |
|------|---------|
| `yoga-video-catalog/data/yoga_videos_enriched.csv` | Main catalog (built by the pipeline). |
| `yoga-video-catalog/config/focus_map.json` | Focus labels → keyword variations. |
| `yoga-video-catalog/config/exclude_keywords.json` | Exclusion rules and focus-based visibility. |

---

## update_from_channels.py {#script-update-from-channels}

**What it does:** Orchestrates the full update. Loads `data/channel_urls.json` and the existing enriched CSV; for each channel, calls the Playwright scraper to get only *new* videos (stops when it hits the first video already in the catalog). Writes new rows to a temp CSV, runs `enrich_videos.py` to fetch metadata via yt-dlp and append to the main CSV, then runs `categorize_data.py` and `update_focus.py` on the full file. Single entry point for "pull new videos and refresh the catalog."

```{r}
#| eval: false
#| file: scripts/update_from_channels.py
```

---

## scrape_channel.py {#script-scrape-channel}

**What it does:** Uses Playwright (Chromium) to open a YouTube channel's Videos page, scrolls until all videos are loaded, and extracts video ID, title, duration, metadata line, and URL from each item. Exposes `scrape_channel_to_list()` for a full scrape and `scrape_channel_new_only()` which stops scrolling once it finds the first video already in a given set (used by the orchestrator to fetch only new videos). Can be run standalone with `--url` and `--output` for one-off scrapes.

```{r}
#| eval: false
#| file: scripts/scrape_channel.py
```

---

## enrich_videos.py {#script-enrich-videos}

**What it does:** Reads a CSV of yoga videos (with a `url` column), uses **yt-dlp** (no API key) to fetch each video's metadata (title, description, duration, upload_date, view_count, etc.), and derives a **focus** column by matching title and description against `config/focus_map.json`. Supports `--append-to` and `--channel` to add a new channel's enriched rows to an existing CSV. Writes both CSV and optional Excel.

```{r}
#| eval: false
#| file: scripts/enrich_videos.py
```

---

## categorize_data.py {#script-categorize-data}

**What it does:** Reads `data/yoga_videos_enriched.csv` and adds derived columns: **duration_mins** and **duration_bucket** (rounded to nearest 5 min, capped at 120), **duration_category** for display; **upload_year** from upload_date; **views_category** (Under 500k, 500k-1M, 1M-2.5M, etc.) and **views_category_order** for sorting. Overwrites the CSV and optional Excel. Run after enrichment so the catalog filters have consistent buckets.

```{r}
#| eval: false
#| file: scripts/categorize_data.py
```

---

## update_focus.py {#script-update-focus}

**What it does:** Recomputes the **focus** column in the enriched CSV using the same keyword logic as `enrich_videos.py` (reads `config/focus_map.json`, matches title + description). Does not call YouTube or yt-dlp - use this after changing the focus map or exclude keywords so existing rows get updated focus tags without re-fetching.

```{r}
#| eval: false
#| file: scripts/update_focus.py
```
::::

:::: {#portfolio-impact .portfolio-view-panel .d-none}
## Impact & Outcome

This project solved a practical personal problem - finding the right yoga video quickly without repeatedly searching multiple channels - and converted it into a reusable data product.

- **Time savings for day-to-day use:** Instead of checking multiple channel pages manually, the catalog centralizes discovery and filtering in one place.
- **Higher quality session matching:** Duration, focus tags, channel controls, keyword search, and year filtering make it easier to choose sessions that match schedule, mobility goals, and training context.
- **Sustainable maintenance:** The incremental update flow (`update_from_channels.py`) lowers upkeep effort and keeps the catalog current without full reprocessing.
- **Reusable architecture:** The same scrape -> enrich -> categorize -> focus -> publish pattern can be adapted to other media catalogs or content-monitoring workflows.
- **Open and extensible:** Because the project is open source and configuration-driven, others can fork it, swap channel lists and focus maps, and build a catalog aligned with their own practice.
- **Portfolio value:** It demonstrates end-to-end ownership - data acquisition, ETL, automation, and UX delivery - on a workflow built for a real, recurring personal use case.
::::

<script>
(function() {
  var productPanel = document.getElementById('portfolio-final-product');
  var overviewPanel = document.getElementById('portfolio-overview');
  var approachPanel = document.getElementById('portfolio-approach');
  var scriptsPanel = document.getElementById('portfolio-scripts');
  var impactPanel = document.getElementById('portfolio-impact');
  var btnProduct = document.querySelector('.portfolio-btn-product');
  var btnOverview = document.querySelector('.portfolio-btn-overview');
  var btnApproach = document.querySelector('.portfolio-btn-approach');
  var btnScripts = document.querySelector('.portfolio-btn-scripts');
  var btnImpact = document.querySelector('.portfolio-btn-impact');
  if (!productPanel || !overviewPanel || !approachPanel || !scriptsPanel || !impactPanel || !btnProduct || !btnOverview || !btnApproach || !btnScripts || !btnImpact) return;

  function setActive(btn) {
    [btnProduct, btnOverview, btnApproach, btnScripts, btnImpact].forEach(function(b) {
      b.classList.remove('btn-primary');
      b.classList.add('btn-outline-primary');
      b.setAttribute('aria-pressed', 'false');
    });
    btn.classList.add('btn-primary');
    btn.classList.remove('btn-outline-primary');
    btn.setAttribute('aria-pressed', 'true');
  }
  function showProduct() {
    productPanel.classList.remove('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnProduct);
  }
  function showOverview() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.remove('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnOverview);
  }
  function showApproach() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.remove('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnApproach);
  }
  function showScripts() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.remove('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnScripts);
  }
  function showImpact() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.remove('d-none');
    setActive(btnImpact);
  }

  btnProduct.addEventListener('click', showProduct);
  btnOverview.addEventListener('click', showOverview);
  btnApproach.addEventListener('click', showApproach);
  btnScripts.addEventListener('click', showScripts);
  btnImpact.addEventListener('click', showImpact);
})();
</script>
