---
title: "Yoga Video Catalog"
---

<div class="yoga-project-page-root" hidden aria-hidden="true"></div>

::: {.yoga-view-toggle role="group" aria-label="Switch view"}
<button type="button" class="btn btn-primary yoga-btn-product" aria-pressed="true">Final product</button>
<button type="button" class="btn btn-outline-primary yoga-btn-overview" aria-pressed="false">Project Overview</button>
<button type="button" class="btn btn-outline-primary yoga-btn-approach" aria-pressed="false">Project Approach</button>
<button type="button" class="btn btn-outline-primary yoga-btn-scripts" aria-pressed="false">Scripts & Code</button>
<button type="button" class="btn btn-outline-primary yoga-btn-impact" aria-pressed="false">Impact & Outcome</button>
:::

::: {#yoga-final-product .yoga-view-panel}
::: {.yoga-embed-bar}
[Open project in new tab](browse.html){.btn .btn-sm .btn-outline-primary target="_blank" rel="noopener"}
:::
::: {#yoga-iframe-wrap .yoga-embed-full}
<iframe src="browse.html" title="Yoga Video Catalog - browse" class="yoga-embed" allowfullscreen style="width:100%;height:100%;position:absolute;left:0;top:0;border:0;"></iframe>
:::
:::

::: {#yoga-overview .yoga-view-panel .d-none}
## Project Overview

### Problem

Yoga content was spread across several YouTube channels. There was no single place to **filter** by length, focus area, recency, or channel, so choosing a session meant repeating the same manual searches.

### Context

I follow a fixed set of trusted instructors and wanted one **personal** catalog that stays current as channels publish new videos-without hand-maintaining spreadsheets.

### Goals

- Centralize videos from a configurable channel list in one browsable catalog.
- Support filters (duration, year, focus, channel, keyword) and a simple **My List** queue in the browser.
- Keep updates **automated** and reproducible (scrape → enrich → publish), not copy-paste.

### Stakeholders

- **Primary user:** me, for day-to-day practice planning.
- **Secondary audience:** portfolio visitors evaluating end-to-end data engineering and front-end delivery.

### Final deliverable

The [**Browse catalog**](browse.html) is the main product: a full-screen, filterable HTML catalog with sliders, chips, search, and a local queue. Implementation details, scripts, and data paths live under **Scripts & Code**.
:::

:::: {#yoga-approach .yoga-view-panel .d-none}
## Project Approach

### Problem Definition

- **Context:** Yoga videos lived across several channels; there was **no** single place to filter by length, focus, or recency.
- **Gap:** I kept redoing manual searches instead of having one reusable view.

### Scope & Assumptions

- **Scope (planned):** personal use; reproducible automation; a fixed list of trusted channels.
- **Assumptions:** channel layouts will stay scrapable; yt-dlp metadata will be enough to tag **focus** without hand-labeling every video.

### Data Sources

- **Planned inputs:** listing fields from each channel’s Videos page (IDs, titles, durations); full metadata via yt-dlp (description, dates, views).
- **Config-only tuning:** `channel_urls.json`, `focus_map.json`, `exclude_keywords.json` (change without editing code).
- **Artifacts:** enriched CSV is the source of truth; Quarto `browse.qmd` reads it plus config JSON for the static browse UI.

### Analytical Design

- **Intent:** a **pipeline**, not a one-off scrape-incremental “new videos only” pulls per channel.
- **Focus rules:** keywords on title + description → deterministic tags.
- **UI plan:** derived buckets for duration and year → sliders and chips on the browse page.
- **Stack (planned):** Python + **Playwright** for listings; **yt-dlp** + pandas for enrichment; **Quarto**, R (CSV → JSON), and vanilla JS for filters and queue-**no YouTube API**.

### Workflow / Process

End-to-end flow from channel list to live catalog:

| Step | What it does |
|------|----------------|
| **1. Configure** | Channel list in `data/channel_urls.json` (display name → channel Videos page URL). |
| **2. Scrape** | `scrape_channel.py` uses Playwright to open each channel’s Videos page, scroll to load items, extract video IDs, titles, durations. |
| **3. Enrich** | `enrich_videos.py` uses yt-dlp for metadata and derives **focus** from title/description via `focus_map.json`. |
| **4. Categorize** | `categorize_data.py` adds duration buckets, upload year, view-count bands. |
| **5. Focus** | `update_focus.py` refreshes focus after config changes (no re-fetch). |
| **6. Update (orchestrator)** | `update_from_channels.py` pulls only **new** videos per channel, appends, then categorizes and updates focus on the full file. |
| **7. Publish** | Render `browse.qmd` so HTML reflects the latest `yoga_videos_enriched.csv`. |

So: **scraping → ETL → categorization → focus → Quarto render** in one repeatable path.

### Constraints & Considerations

- I will respect site terms and rate limits; **no API keys**.
- Layout changes **will** break scrapers sometimes-budget time for fixes.
- Jobs will be **resumable**; exclusions + focus maps will handle QC without row-by-row review.
::::

:::: {#yoga-scripts .yoga-view-panel .d-none}
## Data and config

| Path | Purpose |
|------|---------|
| `yoga-video-catalog/data/yoga_videos_enriched.csv` | Main catalog (built by the pipeline). |
| `yoga-video-catalog/config/focus_map.json` | Focus labels → keyword variations. |
| `yoga-video-catalog/config/exclude_keywords.json` | Exclusion rules and focus-based visibility. |

---

## update_from_channels.py {#script-update-from-channels}

**What it does:** Orchestrates the full update. Loads `data/channel_urls.json` and the existing enriched CSV; for each channel, calls the Playwright scraper to get only *new* videos (stops when it hits the first video already in the catalog). Writes new rows to a temp CSV, runs `enrich_videos.py` to fetch metadata via yt-dlp and append to the main CSV, then runs `categorize_data.py` and `update_focus.py` on the full file. Single entry point for "pull new videos and refresh the catalog."

```{r}
#| eval: false
#| file: scripts/update_from_channels.py
```

---

## scrape_channel.py {#script-scrape-channel}

**What it does:** Uses Playwright (Chromium) to open a YouTube channel's Videos page, scrolls until all videos are loaded, and extracts video ID, title, duration, metadata line, and URL from each item. Exposes `scrape_channel_to_list()` for a full scrape and `scrape_channel_new_only()` which stops scrolling once it finds the first video already in a given set (used by the orchestrator to fetch only new videos). Can be run standalone with `--url` and `--output` for one-off scrapes.

```{r}
#| eval: false
#| file: scripts/scrape_channel.py
```

---

## enrich_videos.py {#script-enrich-videos}

**What it does:** Reads a CSV of yoga videos (with a `url` column), uses **yt-dlp** (no API key) to fetch each video's metadata (title, description, duration, upload_date, view_count, etc.), and derives a **focus** column by matching title and description against `config/focus_map.json`. Supports `--append-to` and `--channel` to add a new channel's enriched rows to an existing CSV. Writes both CSV and optional Excel.

```{r}
#| eval: false
#| file: scripts/enrich_videos.py
```

---

## categorize_data.py {#script-categorize-data}

**What it does:** Reads `data/yoga_videos_enriched.csv` and adds derived columns: **duration_mins** and **duration_bucket** (rounded to nearest 5 min, capped at 120), **duration_category** for display; **upload_year** from upload_date; **views_category** (Under 500k, 500k-1M, 1M-2.5M, etc.) and **views_category_order** for sorting. Overwrites the CSV and optional Excel. Run after enrichment so the catalog filters have consistent buckets.

```{r}
#| eval: false
#| file: scripts/categorize_data.py
```

---

## update_focus.py {#script-update-focus}

**What it does:** Recomputes the **focus** column in the enriched CSV using the same keyword logic as `enrich_videos.py` (reads `config/focus_map.json`, matches title + description). Does not call YouTube or yt-dlp - use this after changing the focus map or exclude keywords so existing rows get updated focus tags without re-fetching.

```{r}
#| eval: false
#| file: scripts/update_focus.py
```
::::

:::: {#yoga-impact .yoga-view-panel .d-none}
## Impact & Outcome

This project solved a practical personal problem - finding the right yoga video quickly without repeatedly searching multiple channels - and converted it into a reusable data product.

- **Time savings for day-to-day use:** Instead of checking channel pages manually, the catalog centralizes discovery and filtering in one place.
- **Higher quality decisions:** Duration, focus tags, and year filters make it easier to choose sessions that match schedule, goals, and energy level.
- **Sustainable maintenance:** The incremental update flow (`update_from_channels.py`) lowers upkeep effort and keeps the catalog current without full reprocessing.
- **Reusable architecture:** The same scrape -> enrich -> categorize -> publish pattern can be adapted to other media collections or content monitoring workflows.
- **Portfolio value:** It demonstrates end-to-end ownership - data acquisition, ETL, automation, and UX delivery - in a production-like workflow that is actually used.
::::

<script>
(function() {
  var productPanel = document.getElementById('yoga-final-product');
  var overviewPanel = document.getElementById('yoga-overview');
  var approachPanel = document.getElementById('yoga-approach');
  var scriptsPanel = document.getElementById('yoga-scripts');
  var impactPanel = document.getElementById('yoga-impact');
  var btnProduct = document.querySelector('.yoga-btn-product');
  var btnOverview = document.querySelector('.yoga-btn-overview');
  var btnApproach = document.querySelector('.yoga-btn-approach');
  var btnScripts = document.querySelector('.yoga-btn-scripts');
  var btnImpact = document.querySelector('.yoga-btn-impact');
  if (!productPanel || !overviewPanel || !approachPanel || !scriptsPanel || !impactPanel || !btnProduct || !btnOverview || !btnApproach || !btnScripts || !btnImpact) return;

  function setActive(btn) {
    [btnProduct, btnOverview, btnApproach, btnScripts, btnImpact].forEach(function(b) {
      b.classList.remove('btn-primary');
      b.classList.add('btn-outline-primary');
      b.setAttribute('aria-pressed', 'false');
    });
    btn.classList.add('btn-primary');
    btn.classList.remove('btn-outline-primary');
    btn.setAttribute('aria-pressed', 'true');
  }
  function showProduct() {
    productPanel.classList.remove('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnProduct);
  }
  function showOverview() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.remove('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnOverview);
  }
  function showApproach() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.remove('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnApproach);
  }
  function showScripts() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.remove('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnScripts);
  }
  function showImpact() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.remove('d-none');
    setActive(btnImpact);
  }

  btnProduct.addEventListener('click', showProduct);
  btnOverview.addEventListener('click', showOverview);
  btnApproach.addEventListener('click', showApproach);
  btnScripts.addEventListener('click', showScripts);
  btnImpact.addEventListener('click', showImpact);
})();
</script>
