---
title: "Offline Geocoding Tool"
---

<div class="yoga-project-page-root" hidden aria-hidden="true"></div>

::: {.yoga-view-toggle role="group" aria-label="Switch view"}
<button type="button" class="btn btn-primary yoga-btn-product" aria-pressed="true">Final product</button>
<button type="button" class="btn btn-outline-primary yoga-btn-overview" aria-pressed="false">Project Overview</button>
<button type="button" class="btn btn-outline-primary yoga-btn-approach" aria-pressed="false">Project Approach</button>
<button type="button" class="btn btn-outline-primary yoga-btn-scripts" aria-pressed="false">Scripts & Code</button>
<button type="button" class="btn btn-outline-primary yoga-btn-impact" aria-pressed="false">Impact & Outcome</button>
:::

::: {#yoga-final-product .yoga-view-panel}
::: {.yoga-embed-bar}
[Open project in new tab](Geocoding_Tool_Showcase.html){.btn .btn-sm .btn-outline-primary target="_blank" rel="noopener"}
:::
::: {#yoga-iframe-wrap .yoga-embed-full}
<iframe src="Geocoding_Tool_Showcase.html" title="Offline Geocoding Tool - Showcase" class="yoga-embed" allowfullscreen style="width:100%;height:100%;position:absolute;left:0;top:0;border:0;"></iframe>
:::
:::

::: {#yoga-overview .yoga-view-panel .d-none}
## Project Overview

### Problem

Statistics Canada's National Address Register (NAR) is the natural reference for authoritative Canadian addresses, but teams often need to geocode **large spreadsheets** (schools, facilities, programs) without sending data to the cloud or opening a GIS desktop.

### Context

Governance and air-gapped environments ruled out consumer geocoding APIs. The work needed a **single, auditable** matcher against NAR with explainable match types and coordinates written back to CSV.

### Goals

- Match input rows to NAR with a **documented hierarchy** (not ad hoc string matching).
- Run **fully offline** after a one-time reference build.
- Support **large files** with resumable batch output and bilingual (EN/FR) address forms.

### Stakeholders

- **Analysts and data stewards** processing sensitive facility or student-address lists.
- **Organizations** that require reproducible, explainable geocoding under strict data-handling rules.

### Final deliverable

An **R pipeline** backed by one **DuckDB** file built from NAR Address + Location: Excel or CSV in, geocoded CSV out, with match type and scores per row. The embedded showcase demonstrates the workflow; full scripts are under **Scripts & Code**. If you are interested in adapting this tool, feel free to reach out.
:::

::: {#yoga-approach .yoga-view-panel .d-none}
## Project Approach

### Problem Definition

- **Context:** Teams had **large spreadsheets** of Canadian addresses (schools, facilities) and **no** lightweight way to geocode them against NAR **without** calling external APIs.
- **Gap:** governance and air-gapped settings ruled out cloud geocoders for this use case.

### Scope & Assumptions

- **Scope (planned):** an R pipeline; **one DuckDB** built from NAR Address + Location; Excel/CSV in → geocoded CSV out.
- **Assumptions:** `LOC_GUID` joins will hold for this workload; EN/FR street variants will normalize through **one** shared map.

### Data Sources

- **Planned load:** NAR Address + Location CSVs → normalized civic/street fields → attach lat/lon per row.
- **Order of operations:** small **test fixtures** first, then production files.

### Analytical Design

- **Planned matcher (literature-based, single hierarchy):** exact full address → exact street only (within same geography) → relaxed (same province/city/postal, attribute relaxation) → fuzzy (narrow pool: province + city + full 6-digit postal or FSA, **composite scoring**: Jaro-Winkler + civic nearness + geographic agreement) → 6-digit postal centroid → FSA centroid → city centroid.
- **Guards:** geography constrained so point matches **do not** cross FSAs or cities inappropriately.
- **Normalization:** street-type and direction handling (including bilingual abbreviations) so input and reference stay comparable.
- **Scale:** single DuckDB connection; batched fuzzy queries with configurable pool size; streamed CSV output for memory discipline.

### Workflow / Process

1. **One-time build:** join NAR Address + Location on `LOC_GUID`, normalize fields, write table `ref` to `nar.duckdb`.  
2. **Production geocode:** read Excel/CSV with expected address columns; process in chunks (e.g. 100 rows) with **append-after-each-chunk** so runs are resumable.  
3. **After NAR refresh:** optional regression test script on fixtures before full production files.  

### Constraints & Considerations

- Execution stays **fully offline**; large files will need **memory** discipline.
- Bilingual address forms will need **consistent** normalization.
- Every row will carry **match type + scores** so analysts can explain results **without** a GIS desktop.
:::

::: {#yoga-scripts .yoga-view-panel .d-none}
## build_nar_duckdb.R {#script-build-nar}

**What it does:** One-time build of the NAR DuckDB. Reads all Location CSVs into a temporary `loc` table (LOC_GUID, lat/lon), then streams Address CSVs in chunks, joins to `loc` on LOC_GUID, normalizes province (SGC → 2-letter), city, postal, FSA, and full address. Writes table `ref` with columns expected by the geocoder (Latitude, Longitude, Full_Address, Civic_Number, street fields, city_norm, fsa, address_norm, street_only_norm). Drops `loc` when done.

```{r}
#| file: R/build_nar_duckdb.R
#| eval: false
```

---

## query_ref_duckdb.R {#script-query-ref}

**What it does:** DuckDB query helpers for the geocoder. `get_ref_empty_template()` returns a 0-row tibble with ref schema. `query_ref_exact()` and `query_ref_exact_street()` match on normalized full address or street-only norm. `query_ref_exact_street_in_geography()` restricts exact-street matches to the same province + city + postal/FSA. `query_ref_candidates_narrow()` fetches the candidate pool for fuzzy matching (province, city, full postal or FSA; optional street prefix). `query_ref_postal_centroid()`, `query_ref_fsa_centroid()`, and `query_ref_city_centroid()` return one centroid row each for fallback matching.

```{r}
#| file: R/query_ref_duckdb.R
#| eval: false
```

---

## utils_geocode.R {#script-utils-geocode}

**What it does:** Normalization and scoring utilities. Province and city name normalization (including StatCan CSD suffixes and "City of" prefixes); street-type normalization via STREET_TYPE_MAP; cardinal directions; Canadian postal (6-char). `parse_address_components()` splits an address string into civic number, street part, city, province, postal. `build_relaxed_address_norms()` builds variants (drop trailing direction, then street type) for relaxed matching. Text similarity (Jaro-Winkler), numeric nearness (civic numbers), and geographic score feed into `composite_score()` for fuzzy ranking.

```{r}
#| file: R/utils_geocode.R
#| eval: false
```

---

## street_type_map.R {#script-street-type-map}

**What it does:** Canonical street-type map: full words and abbreviations (English and French) to a single lowercase code (Canada Post / StatCan NAR). Used by `normalize_street_types_in_string()` so "avenue", "av", "ave" and "rue" match consistently across input and reference.

```{r}
#| file: R/street_type_map.R
#| eval: false
```

---

## geocode_ref.R {#script-geocode-ref}

**What it does:** Core geocoding function. Implements the full hierarchy: (1) exact full address, (2) exact street within same geography, (3) relaxed (variant norms in narrow pool), (4) fuzzy (narrow pool, composite score, configurable threshold and min street score), (5) 6-digit postal centroid, (6) FSA centroid, (7) city centroid. Uses optional first-character filter and street-direction filter to shrink the candidate set. Returns a tibble with match_type, scores, and ref columns. Single DuckDB connection; batched by (province, city, postal/FSA) for low memory.

```{r}
#| file: R/geocode_ref.R
#| eval: false
```

---

## geocode_excel_file.R {#script-geocode-excel}

**What it does:** User-facing entry point. Reads Excel or CSV from a given path, drops rows with no usable address, calls `geocode_ref()` in chunks (e.g. 100 rows), and appends to output CSV after each chunk so progress is saved and runs can be resumed. Column names for address parts are configurable (`address_cols`). Output is written to `output/<basename>_geocoded.csv` by default. Forwards options (e.g. `fuzzy_threshold`, `max_candidate_pool`) to `geocode_ref()`.

```{r}
#| file: geocode_excel_file.R
#| eval: false
```

---

## run_build_nar_duckdb.R {#script-run-build}

**What it does:** One-time runner. Sets project root, sources `R/utils_geocode.R` and `R/build_nar_duckdb.R`, and calls `build_nar_duckdb(nar_dir, db_path)` to produce `data/nar.duckdb`. Run once (or when NAR data changes).

```{r}
#| file: run_build_nar_duckdb.R
#| eval: false
```

---

## run_test_geocode.R {#script-run-test}

**What it does:** Test run. Sources `geocode_excel_file.R` and runs `geocode_excel()` on `data/ungeocoded_files/test_addresses.csv` (or .xlsx), writing to `output/test_addresses_geocoded.csv`. Use after building the NAR DB and creating test addresses (e.g. via `create_test_addresses.R`).

```{r}
#| file: run_test_geocode.R
#| eval: false
```

---

## run_geocode.R {#script-run-geocode}

**What it does:** Production run. Sources `geocode_excel_file.R` and runs `geocode_excel()` on the SIF school data file (or another configured path), writing to `output/<basename>_geocoded.csv`. Re-run to resume from last saved chunk.

```{r}
#| file: run_geocode.R
#| eval: false
```

---

## create_test_addresses.R {#script-create-test}

**What it does:** Creates a small CSV of test addresses in `data/ungeocoded_files/test_addresses.csv` for use with `run_test_geocode.R`. Optional helper when no real input file is available.

```{r}
#| file: create_test_addresses.R
#| eval: false
```

---

See the [README](README.md) in this project for setup, NAR data layout, and usage.
:::

::: {#yoga-impact .yoga-view-panel .d-none}
## Impact & Outcome

This project enabled reliable geocoding in privacy-constrained environments where cloud APIs are not acceptable. It improved confidence in address linkage quality while keeping the workflow auditable and repeatable.

- **Who it helped:** Teams handling sensitive address datasets in offline or restricted environments.
- **What it helped with:** High-volume geocoding, transparent match-level reporting, and reduced dependence on external services.
- **Why it matters:** It delivers practical data quality improvements without compromising governance or privacy requirements.
- **Operational benefits:** Fully offline execution, deterministic hierarchy for audit, tunable fuzzy behaviour, and EN/FR address consistency without a GIS desktop.

If you are interested in adapting this tool for your own project, feel free to reach out.
:::

<script>
(function() {
  var productPanel = document.getElementById('yoga-final-product');
  var overviewPanel = document.getElementById('yoga-overview');
  var approachPanel = document.getElementById('yoga-approach');
  var scriptsPanel = document.getElementById('yoga-scripts');
  var impactPanel = document.getElementById('yoga-impact');
  var btnProduct = document.querySelector('.yoga-btn-product');
  var btnOverview = document.querySelector('.yoga-btn-overview');
  var btnApproach = document.querySelector('.yoga-btn-approach');
  var btnScripts = document.querySelector('.yoga-btn-scripts');
  var btnImpact = document.querySelector('.yoga-btn-impact');
  if (!productPanel || !overviewPanel || !approachPanel || !scriptsPanel || !impactPanel || !btnProduct || !btnOverview || !btnApproach || !btnScripts || !btnImpact) return;

  function setActive(btn) {
    [btnProduct, btnOverview, btnApproach, btnScripts, btnImpact].forEach(function(b) {
      b.classList.remove('btn-primary');
      b.classList.add('btn-outline-primary');
      b.setAttribute('aria-pressed', 'false');
    });
    btn.classList.add('btn-primary');
    btn.classList.remove('btn-outline-primary');
    btn.setAttribute('aria-pressed', 'true');
  }
  function showProduct() {
    productPanel.classList.remove('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnProduct);
  }
  function showOverview() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.remove('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnOverview);
  }
  function showApproach() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.remove('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnApproach);
  }
  function showScripts() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.remove('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnScripts);
  }
  function showImpact() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.remove('d-none');
    setActive(btnImpact);
  }

  btnProduct.addEventListener('click', showProduct);
  btnOverview.addEventListener('click', showOverview);
  btnApproach.addEventListener('click', showApproach);
  btnScripts.addEventListener('click', showScripts);
  btnImpact.addEventListener('click', showImpact);
})();
</script>
