---
title: "Offline Geocoding Tool"
---

<div class="portfolio-project-page-root" hidden aria-hidden="true"></div>

::: {.portfolio-view-toggle role="group" aria-label="Switch view"}
<button type="button" class="btn btn-primary portfolio-btn-product" aria-pressed="true">Final product</button>
<button type="button" class="btn btn-outline-primary portfolio-btn-overview" aria-pressed="false">Project Overview</button>
<button type="button" class="btn btn-outline-primary portfolio-btn-approach" aria-pressed="false">Project Approach</button>
<button type="button" class="btn btn-outline-primary portfolio-btn-scripts" aria-pressed="false">Scripts & Code</button>
<button type="button" class="btn btn-outline-primary portfolio-btn-impact" aria-pressed="false">Impact & Outcome</button>
:::

::: {.portfolio-page-intro}
::: {.portfolio-accent-rule}
:::
Offline geocoding workflow designed for sensitive Canadian address data, with deterministic matching and transparent fallback logic.
:::

::: {.portfolio-meta-row}
[Privacy-safe geocoding]{.portfolio-meta-chip}
[Deterministic address matching]{.portfolio-meta-chip}
[Reproducible geocoding pipeline]{.portfolio-meta-chip}
:::

::: {#portfolio-final-product .portfolio-view-panel}
::: {.portfolio-embed-bar}
[Open project in new tab](Geocoding_Tool_Showcase.html){.btn .btn-sm .btn-outline-primary target="_blank" rel="noopener"}
:::
::: {#portfolio-iframe-wrap .portfolio-embed-full}
<iframe src="Geocoding_Tool_Showcase.html" title="Offline Geocoding Tool - Showcase" class="portfolio-embed" allowfullscreen style="width:100%;height:100%;position:absolute;left:0;top:0;border:0;"></iframe>
:::
:::

::: {#portfolio-overview .portfolio-view-panel .d-none}
## Project Overview

### Problem

In an early Statistics Canada assignment, I needed to estimate distances between survey respondents and local data-collection facilities across 16 Canadian cities. That required geocoding respondent addresses, but cloud APIs and commercial platforms were not an option because the records were highly sensitive.

### Context

Address quality varied widely across large and small cities, and source formats were not standardized to existing internal street-reference files. A direct join against pre-existing XY-enabled datasets was therefore unreliable, so the work needed a dataset-specific geocoder that could run offline and still produce auditable outputs.

### Goals

- Support offline geocoding for sensitive records without external API calls.
- Match inconsistent street-address inputs using a documented hierarchy rather than ad hoc one-off rules.
- Produce explainable outputs (match types, scores, coordinates) so analysts can validate results before downstream distance analysis.

### Stakeholders

- **Applied analysts and survey teams:** geocoding respondent or facility addresses for spatial analysis tasks.
- **Organizations with strict governance:** teams that need reproducible geocoding workflows for protected datasets.

### Final deliverable

The original geocoding tool (not shown here) reached high match coverage for its specific workload, but that version was later lost when the project Virtual Machine (VM) became corrupt. This portfolio rebuild prioritizes portability and reuse: an R + DuckDB pipeline using NAR Address + Location (Excel/CSV in, geocoded CSV out) with documented match logic, row-level diagnostics, and offline execution. The embedded showcase demonstrates the workflow, and full scripts are listed under Scripts & Code.
:::

::: {#portfolio-approach .portfolio-view-panel .d-none}
## Project Approach

### Problem Definition

- **Context:** The initial use case was distance analysis for survey operations across 16 cities, where respondent addresses needed coordinate assignment under strict privacy controls.
- **Gap:** Address strings were inconsistent and not directly joinable to existing internal files, while cloud geocoders were not permitted in the working environment.

### Scope & Assumptions

- **Scope:** A fully offline R workflow backed by one DuckDB reference built from NAR Address + Location, with standardized input handling and reproducible CSV outputs.
- **Assumptions:** `LOC_GUID` joins remain stable for reference construction; EN/FR street variants can be normalized through a shared mapping layer; match quality improves when project-specific tuning is applied.

### Data Sources

- **Reference data:** NAR Address + Location CSVs are joined and normalized into one local table with coordinate fields.
- **Workload reality:** Input datasets can vary by city size and formatting quality, so preprocessing and staged matching are essential before final coordinate assignment.

### Analytical Design

- **Matcher hierarchy:** exact full address -> exact street only (within same geography) -> relaxed (same province/city/postal with controlled attribute relaxation) -> fuzzy (narrow candidate pool with composite scoring: Jaro-Winkler + civic-number nearness + geographic agreement) -> 6-digit postal centroid -> FSA centroid -> city centroid.
- **Guards:** geography constrained so point matches do not cross FSAs or cities inappropriately.
- **Normalization:** street-type and direction handling (including bilingual abbreviations) so input and reference stay comparable.
- **Trade-off:** The original internal build was highly tuned to one dataset and achieved stronger accuracy; this portfolio version is intentionally more general and therefore requires optional dataset-specific rule tuning for best performance.

### Workflow / Process

1. **One-time build:** join NAR Address + Location on `LOC_GUID`, normalize key fields, and write table `ref` to `nar.duckdb`.  
2. **Geocode run:** read Excel/CSV inputs, process in chunks, and append output incrementally so runs are resumable.  
3. **Quality review:** inspect match types and scores, then apply project-specific threshold or rule refinements where needed.  
4. **Validation:** compare geocoded points against known locations or mapped reference checks before final analytical use.  

### Constraints & Considerations

- Execution stays fully offline; large files will need memory discipline.
- Bilingual address forms will need consistent normalization.
- This general-purpose build can be less accurate than a narrowly tuned one, so local rule customization remains an expected part of production use.
- Every row carries match type and scores so analysts can explain and audit results without a GIS desktop.
:::

::: {#portfolio-scripts .portfolio-view-panel .d-none}
## build_nar_duckdb.R {#script-build-nar}

**What it does:** One-time build of the NAR DuckDB. Reads all Location CSVs into a temporary `loc` table (LOC_GUID, lat/lon), then streams Address CSVs in chunks, joins to `loc` on LOC_GUID, normalizes province (SGC → 2-letter), city, postal, FSA, and full address. Writes table `ref` with columns expected by the geocoder (Latitude, Longitude, Full_Address, Civic_Number, street fields, city_norm, fsa, address_norm, street_only_norm). Drops `loc` when done.

```{r}
#| file: R/build_nar_duckdb.R
#| eval: false
```

---

## query_ref_duckdb.R {#script-query-ref}

**What it does:** DuckDB query helpers for the geocoder. `get_ref_empty_template()` returns a 0-row tibble with ref schema. `query_ref_exact()` and `query_ref_exact_street()` match on normalized full address or street-only norm. `query_ref_exact_street_in_geography()` restricts exact-street matches to the same province + city + postal/FSA. `query_ref_candidates_narrow()` fetches the candidate pool for fuzzy matching (province, city, full postal or FSA; optional street prefix). `query_ref_postal_centroid()`, `query_ref_fsa_centroid()`, and `query_ref_city_centroid()` return one centroid row each for fallback matching.

```{r}
#| file: R/query_ref_duckdb.R
#| eval: false
```

---

## utils_geocode.R {#script-utils-geocode}

**What it does:** Normalization and scoring utilities. Province and city name normalization (including StatCan CSD suffixes and "City of" prefixes); street-type normalization via STREET_TYPE_MAP; cardinal directions; Canadian postal (6-char). `parse_address_components()` splits an address string into civic number, street part, city, province, postal. `build_relaxed_address_norms()` builds variants (drop trailing direction, then street type) for relaxed matching. Text similarity (Jaro-Winkler), numeric nearness (civic numbers), and geographic score feed into `composite_score()` for fuzzy ranking.

```{r}
#| file: R/utils_geocode.R
#| eval: false
```

---

## street_type_map.R {#script-street-type-map}

**What it does:** Canonical street-type map: full words and abbreviations (English and French) to a single lowercase code (Canada Post / StatCan NAR). Used by `normalize_street_types_in_string()` so "avenue", "av", "ave" and "rue" match consistently across input and reference.

```{r}
#| file: R/street_type_map.R
#| eval: false
```

---

## geocode_ref.R {#script-geocode-ref}

**What it does:** Core geocoding function. Implements the full hierarchy: (1) exact full address, (2) exact street within same geography, (3) relaxed (variant norms in narrow pool), (4) fuzzy (narrow pool, composite score, configurable threshold and min street score), (5) 6-digit postal centroid, (6) FSA centroid, (7) city centroid. Uses optional first-character filter and street-direction filter to shrink the candidate set. Returns a tibble with match_type, scores, and ref columns. Single DuckDB connection; batched by (province, city, postal/FSA) for low memory.

```{r}
#| file: R/geocode_ref.R
#| eval: false
```

---

## geocode_excel_file.R {#script-geocode-excel}

**What it does:** User-facing entry point. Reads Excel or CSV from a given path, drops rows with no usable address, calls `geocode_ref()` in chunks (e.g. 100 rows), and appends to output CSV after each chunk so progress is saved and runs can be resumed. Column names for address parts are configurable (`address_cols`). Output is written to `output/<basename>_geocoded.csv` by default. Forwards options (e.g. `fuzzy_threshold`, `max_candidate_pool`) to `geocode_ref()`.

```{r}
#| file: geocode_excel_file.R
#| eval: false
```

---

## run_build_nar_duckdb.R {#script-run-build}

**What it does:** One-time runner. Sets project root, sources `R/utils_geocode.R` and `R/build_nar_duckdb.R`, and calls `build_nar_duckdb(nar_dir, db_path)` to produce `data/nar.duckdb`. Run once (or when NAR data changes).

```{r}
#| file: run_build_nar_duckdb.R
#| eval: false
```

---

## run_test_geocode.R {#script-run-test}

**What it does:** Test run. Sources `geocode_excel_file.R` and runs `geocode_excel()` on `data/ungeocoded_files/test_addresses.csv` (or .xlsx), writing to `output/test_addresses_geocoded.csv`. Use after building the NAR DB and creating test addresses (e.g. via `create_test_addresses.R`).

```{r}
#| file: run_test_geocode.R
#| eval: false
```

---

## run_geocode.R {#script-run-geocode}

**What it does:** Production run. Sources `geocode_excel_file.R` and runs `geocode_excel()` on the SIF school data file (or another configured path), writing to `output/<basename>_geocoded.csv`. Re-run to resume from last saved chunk.

```{r}
#| file: run_geocode.R
#| eval: false
```

---

## create_test_addresses.R {#script-create-test}

**What it does:** Creates a small CSV of test addresses in `data/ungeocoded_files/test_addresses.csv` for use with `run_test_geocode.R`. Optional helper when no real input file is available.

```{r}
#| file: create_test_addresses.R
#| eval: false
```

---

See the [README](README.md) in this project for setup, NAR data layout, and usage.
:::

::: {#portfolio-impact .portfolio-view-panel .d-none}
## Impact & Outcome

This project demonstrates a practical path for geocoding sensitive address data in environments where cloud services are not acceptable. It combines deterministic matching, transparent fallback logic, and reproducible outputs so teams can balance privacy, scalability, and quality control.

- **Who it helped:** Analysts and organizations processing protected address datasets under strict governance constraints.
- **What it helped with:** Offline geocoding across varied address quality, with match-level reporting that supports audit and review.
- **Why it matters:** It shows how a custom geocoding workflow can remain useful even when the original internal implementation is no longer available, while still preserving the core privacy-first design.
- **Operational benefits:** Fully offline execution, deterministic hierarchy, tunable fuzzy behavior, and EN/FR normalization support for repeatable production runs.

If you are interested in adapting this tool for your own project, feel free to reach out.
:::

<script>
(function() {
  var productPanel = document.getElementById('portfolio-final-product');
  var overviewPanel = document.getElementById('portfolio-overview');
  var approachPanel = document.getElementById('portfolio-approach');
  var scriptsPanel = document.getElementById('portfolio-scripts');
  var impactPanel = document.getElementById('portfolio-impact');
  var btnProduct = document.querySelector('.portfolio-btn-product');
  var btnOverview = document.querySelector('.portfolio-btn-overview');
  var btnApproach = document.querySelector('.portfolio-btn-approach');
  var btnScripts = document.querySelector('.portfolio-btn-scripts');
  var btnImpact = document.querySelector('.portfolio-btn-impact');
  if (!productPanel || !overviewPanel || !approachPanel || !scriptsPanel || !impactPanel || !btnProduct || !btnOverview || !btnApproach || !btnScripts || !btnImpact) return;

  function setActive(btn) {
    [btnProduct, btnOverview, btnApproach, btnScripts, btnImpact].forEach(function(b) {
      b.classList.remove('btn-primary');
      b.classList.add('btn-outline-primary');
      b.setAttribute('aria-pressed', 'false');
    });
    btn.classList.add('btn-primary');
    btn.classList.remove('btn-outline-primary');
    btn.setAttribute('aria-pressed', 'true');
  }
  function showProduct() {
    productPanel.classList.remove('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnProduct);
  }
  function showOverview() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.remove('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnOverview);
  }
  function showApproach() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.remove('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnApproach);
  }
  function showScripts() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.remove('d-none');
    impactPanel.classList.add('d-none');
    setActive(btnScripts);
  }
  function showImpact() {
    productPanel.classList.add('d-none');
    overviewPanel.classList.add('d-none');
    approachPanel.classList.add('d-none');
    scriptsPanel.classList.add('d-none');
    impactPanel.classList.remove('d-none');
    setActive(btnImpact);
  }

  btnProduct.addEventListener('click', showProduct);
  btnOverview.addEventListener('click', showOverview);
  btnApproach.addEventListener('click', showApproach);
  btnScripts.addEventListener('click', showScripts);
  btnImpact.addEventListener('click', showImpact);
})();
</script>
